Draft Documents

### 2022-11-16 src/draft.Rmd
f6

Only some of the linear models that have been explored are showed.
```{r cars}
summary(lm(formula = pov ~ income,data = train)) #0.6201
```
Since income as a predictor brought the highest adjusted r-value, we add another predictor to income to find the predictor added to income which produced the highest adjusted r-value. reg as a predictor has the highest adjusted r-value=0.7181

@@

The forward selection process continues and lgdp.pc is the new predictor added that produced highest adjusted r-square=0.7492
```{r}
summary(lm(formula = pov ~ lgdp.pc+income+reg,data = train)) #0.7492
```
The addition of predictor gdp.pc produces the highest adjusted r-square value above 0.75, adjusted r-square=0.7703
```{r}
summary(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)) #0.7703
```

@@

  data.frame(
    MSE = mse,
    MAE = mae,
    RMSE = rmse,
    MAPE = mape
  )
}
predicted<-predict(lm1,newdata=test)
actual<-test$pov
df23<-na.omit(data.frame(actual,predicted))
ac<-df23$actual
pr<-df23$predicted
eval.metrics.linreg(ac,pr)
```
###  3.3.3. Interpretation
gdp per capital, income class and region of the country can provide a model to predict the poverty headcount ratio in a country.

>>>>

```{r cars}
summary(lm(formula = pov ~ income,data = train)) #0.6201
```

Since income as a predictor brought the highest adjusted r-value, we add another predictor to income to find the predictor added to income which produced the highest adjusted r-value. reg as a predictor has the highest adjusted r-value=0.7181

@@

The forward selection process continues and lgdp.pc is the new predictor added that produced highest adjusted r-square=0.7492
```{r}
summary(lm(formula = pov ~ lgdp.pc+income+reg,data = train)) #0.7492
```

The addition of predictor gdp.pc produces the highest adjusted r-square value above 0.75, adjusted r-square=0.7703
```{r}
summary(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)) #0.7703
```

@@

  data.frame(
    MSE = mse,
    MAE = mae,
    RMSE = rmse,
    MAPE = mape
  )
}
predicted<-predict(lm1,newdata=test)
actual<-test$pov
df23<-na.omit(data.frame(actual,predicted))
ac<-df23$actual
pr<-df23$predicted
eval.metrics.linreg(ac,pr)
```

###  3.3.3. Interpretation
gdp per capital, income class and region of the country can provide a model to predict the poverty headcount ratio in a country.
